Security Audit of Safeplug

### 2014-02-20 w2sp/report.tex
added intro/conclusion and new images, table

\section{Introduction}
% no \IEEEPARstart
User privacy is becoming increasingly important as more Internet users realize how vulnerable they are to attackers and eavesdroppers.  This has been exacerbated by the current news about the NSA's surveillance of the Internet~\cite{nsa}.  Unfortunately, the average Internet user is not aware of how to protect themselves against malicious users.

@@

@@

%%TODO: A table for platform and browsers available?

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.7\textwidth]{latency2}
  \caption{Latency of web requests.}
  \label{fig:latency2}
\end{figure*}

@@

Ultimately, the structural concerns of the Safeplug ``Torifying proxy-in-a-box'' strategy indicate that this is not the correct method for security and anonymity online.  It is critical for Safeplug to correct their engineering errors, particularly the vulnerability to silent disabling of Tor in order to protect customers who have already made use of the device, but users who are truly concerned about safety and anonymity online should make use of technologies directly from the Tor Project.

@@

>>>>

\section{Introduction}
% no \IEEEPARstart

Privacy on the Internet is becoming increasingly important as more users realize how vulnerable they are to being surveilled and attacked; anonymity has become the goal for many Internet users in order to protect themselves.  A recent study has shown that people have been the victim of many security-related issues, such as compromised emails/accounts, harrassment, stolen Social Security Number, bank information, and credit card numbers, due to their online visibility~\cite{pew}.  As the Internet grows and the amount of user information that is collected and/or provided online increases, users will continue to be more vulnerable.  According to this study, 86\% of internet users have tried to become more anonymous online by either clearing cookies, encrypting their email, or using virtual networks that mask their IP address~\cite{pew}.  While this study shows that a large percentage of users are taking measures to reduce their visibility online, 59\% reported that they don't believe it is possible to become completely anonymous online~\cite{pew}.

The cloud storage company, Pogoplug, noticed the demand for online anonymity, and in November of 2013 they released the Safeplug.  This device is a small box that plugs into a user's home router and by routing all traffic through Tor, it claims to: conceal your identity, hide where you live, shield your surfing habits, and make you anonymous online~\cite{pogo}.  A device such as this should be audited to confirm or deny the validity of such bold claims.  We conducted the first public third-party security audit of the Safeplug by analyzing the hardware, software, and network behavior.  The following are some of our findings:

\begin{itemize}
\item The presence of both first- and third-party tracking cookies.
\item A Cross-Site Request Forgery (CSRF) vulnerability that allows an outside attacker to modify the Safeplug settings (i.e., turning Tor on/off, turning ad-blocking on/off, turning the Tor relay on/off, adding/removing whitelisted sites from Tor).
\item A vulnerability that allows an attacker within the network to modify the Safeplug settings without notifying any other devices on the network of the change.
\item A higher latency than that of the Tor Browser Bundle.
\end{itemize}

While we found severe engineering vulnerabilities and a weak market, Pogoplug had good intentions and goals for their device.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=.6\textwidth]{safeplug_flowchart}
\caption{Flowchart.}
\label{fig:instructions}
\end{center}
\end{figure*}

@@

%%TODO: verify these
\begin{center}
	\begin{tabular}{|c|c|c|}
	\hline
		Platform & Browsers \\ \hline
		Windows	& Internet Explorer, Firefox \\ \hline
		OSX & Safari, Firefox \\ \hline
		iOS	& Safari \\ \hline
		Android	& Firefox\\ \hline
	\end{tabular}
\end{center}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.7\textwidth]{graph2}
  \caption{Latency of web requests.}
  \label{fig:latency2}
\end{figure*}

@@

\section{Conclusion}
Ultimately, the structural concerns of the Safeplug ``Torifying proxy-in-a-box'' strategy indicate that this is not the correct method for security and anonymity online.  It is critical for Safeplug to correct their engineering errors, particularly the vulnerability to silent disabling of Tor in order to protect customers who have already made use of the device, but users who are truly concerned about safety and anonymity online should make use of technologies directly from the Tor Project.

@@

\bibitem{pew} Pew Research Center.  ``Anonymity, Privacy, and Security Online.'', \url{http://www.pewinternet.org/files/old-media//Files/Reports/2013/PIP_AnonymityOnline_090513.pdf}.

\bibitem{pogo} Pogoplug. ``Pogoplug'', \url{https://pogoplug.com}.
